Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Explain no_vulgarity

\subsubsection{no\_vulgarity}
\label{subs:no_vulgarity}

>>>>

\subsubsection{no\_vulgarity}
\label{subs:no_vulgarity}
A commit message should obviously not contain any vulgarity for many reasons, but it should suffice to say that such things are unprofessional and will rarely make the commit any better.

Checking for vulgarity is done with a perl module \footnote{http://search.cpan.org/~abigail/Regexp-Common-2013031301/lib/Regexp/Common/profanity.pm} that contains a list of offensive words. The test for the criterion is passed if none of the words are found in the commit message.

This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}
